---
title: "Week 04 Questions"
author: "Sarah Tanja"
date: "4/18/2023"
output: 
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

a)  **What is `tmux` and how does this relate to our current way of working on raven?**

`tmux` is terminal multiplexing in Unix (or Unix-like) Operating Systems (OS). It allows multiple 'terminals' or 'windows' to be accessed simultaneously, and to run independent of each other. It relates to our work on the `raven` server because when each of us is using our own account and working on our own terminal on the same machine it must be doing it through something like `tmux`.

b)  **What is `ssh` and what would the code be you would type if you were going to `ssh` into raven?**

`ssh` is secure shell, and is an encrypted network protocol for connecting to a computer. It allows remote login and unix-based command line execution. 

To connect to `raven` I would type:

```{r, engine='bash'}
ssh stanja@raven.fish.washington.edu
```

To connect to `mox-hyak` I would type:
```{r, engine='bash'}
ssh stanja@mox.hyak.uw.edu
```


c)  **What has been the most challenging part of your research project? Are you happy with your organization skills? If not what could be improved?**

The most challenging part is getting my own data... but aside from that (and related to this course) I've been struggling a little with hashes. I downloaded some metadata from Ariana Huffmyer's GitHub repo and have been using `md5sum` to check it... while the .csv files are the same, the hash on one is off by a single hexadecimal character.

Am I happy with my organizational skills? Yes. However, I find I spend a lot of time, maybe too much time, trying to research 'The Way' to do something, and there are so many options and no clear best. As soon as I learn about one option, another pops onto my RADAR that seems better. I think I can improve this by just sticking with what I've got instead of constantly trying to re-work what I've already done into something else (i.e. shifting RMarkdown to Quarto, shifting Jekyll open lab notebook to a Quarto blog).

c)  **For last weeks assignment what did you appreciate the most about knitting documents?**

`cache=TRUE` was a really useful chunk option to learn about! It makes it so that you can display output like pretty graphs without re-running those long processes.
