---
title: "Week 05 Questions"
author: "Sarah Tanja"
date: "4/25/2023"
output: 
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### What is Quarto?

Quarto is very similar to RMarkdown, and was built by the same people. Why use Quarto over RMarkdown? It uses Pandoc to be compatible with rendering many different output formats. It has a few more advanced features than RMarkdown, I particularly like the `::: callout-info :::` code wrap that automatically highlights and formats text for different purposes (info, warning, caution, danger). There are also many themes and

### How do you make columns using Revealjs in Quarto Presentations?

> To put material in side by side columns, you can use a native div container with class `.columns`, containing two or more div containers with class `.column` and a `width` attribute:

```{r}
:::: {.columns}

::: {.column width="40%"}

Left column

:::

::: {.column width="60%"}

Right column

:::

::::

```

### How would you change the appearance of slides using Revealjs in Quarto Presentations?

There seem to be many ways to customize slides using `Revealjs`... you can customize slides by making the background an image or a video. Themes are probably the easiest uniform way to change slide appearance. There are 10 built-in themes, or you can create your own. Here is the full list of available themes:

beige

blood

dark

default

league

moon

night

serif

simple

sky

solarized

### What has been the biggest constraint working on your own research project in the past week?

Time. I have been in the lab working on DNA/RNA extractions and have spent less time working on developing the DGE script for *Montipora capitata* rice coral.
