---
title: "04-hyak-mox"
format: html
---

# **Setup**

1.  Go to <https://uwnetid.washington.edu/manage/>

2.  Click the \"Computing Services\" link on the left

3.  Click the \"Hyak Server\" and \"Lolo Server\" check boxes in the \"Inactive Services\" section.

4.  Click the \"Subscribe \>\" button at the bottom of the page.

5.  Read the notice and click the \"Finish\" button.

For two factor authentication, you can either sign up for Duo [here](https://identity.uw.edu/2fa/) and use your smart phone or request a security token [here](http://www.washington.edu/itconnect/service/authentication/). Duo is much easier.

# **Logging in**

1.  Open your favorite terminal

2.  Type `ssh stanja@mox.hyak.uw.edu` 

3.  Input your UWNetID *password*

4.  If you\'re signed up for 2-factor authentication via Duo, open your smart phone and approve the connection.

5.  You\'re logged in to a Login node for Hyak!

# **Running a job**

Once logged into mox, navigate to `/gscratch/scrubbed/stanja`.

```{r, engine='bash'}
cd /gscratch/scrubbed/stanja

```

If the dir is not there you shoud create it. For every job you submit I recommend working within a directory. Usually I name these in a data format, but we can just `mkdir assign_04`.

### Generate shell script

To run a job you need to generate a shell script. 
In Rstudio, go to `File>New File> Shell Script`
Save the shell script in your code directory and name it `04-job.sh`
Add contents such as:

```{r}
#!/bin/bash
## blast
#SBATCH --job-name=blast
## Allocation Definition
#SBATCH --account=srlab
#SBATCH --partition=srlab
## Resources
## Nodes
#SBATCH --nodes=1
## Walltime (days-hours:minutes:seconds format)
#SBATCH --time=01-08:00:00
## Memory per node
#SBATCH --mem=100G
#SBATCH --mail-type=ALL
#SBATCH --mail-user=stanja@uw.edu
## Specify the working directory for this job
#SBATCH --chdir=/gscratch/scrubbed/stanja/blast

#run a python script you wrote!
module load intel-python3_2017

python 04-hello.py

# run blastx just to get manual
/gscratch/srlab/programs/ncbi-blast-2.10.1+/bin/blastx \

#a few bash commands
pwd 

whoami

echo "yah! I did it!!!!!!!!!!"

#this writes out  tofile
echo "yah! I did it!!!!!!!!!!" > text.file
```

### create Python Script

In Rstudio, navigate to `File > New File > Python Script`
Create a Python Script and name it 04-hello.py with the contents:

```
print("Hello, World!")

```
Save this script in the same directory as the `04-job.sh`

Now we want to move these two files to mox into the assign_04 directory. To to this you will need to type something to the effect of the following in the terminal

rsync -avz assignments/code/04-* sr320@mox.hyak.uw.edu:/gscratch/scrubbed/sr320/assign_04

